Growing Up With Nell: A Narrative Interface for Literacy

### 2012-04-23 paper.tex
Further tweaks to reduce external dependencies and conform to final style.
Inline .bib file to create "self-contained" .tex, per ACM instructions.
The eps figures are not inlined, I guess that's okay.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%\documentclass{acm_proc_article-sp}
\documentclass[preprint]{sig-alternate}
\usepackage{url}
\usepackage{ifthen}\newboolean{noauthors}\setboolean{noauthors}{false}
\hyphenation{Web-GL Java-Script Turtle-Script infra-structure}

\begin{document}\toappear{}

@@

\ifthenelse{\boolean{noauthors}}{}{
\numberofauthors{1}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. Scott Ananian \qquad Chris J. Ball \qquad Michael Stone\titlenote{%
Now at Akamai Technologies.}\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{\{cscott,cjb,mstone\}@laptop.org}
%\and  % use '\and' if you need 'another row' of author names
}
}
\date{12 March 2012}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

% Copyright info
\toappear{\textit{IDC 2012}, June 12--15, 2012, Bremen, Germany.\\
Copyright 2012 ACM 978-1-4503-1007-9\ldots\$10.00.}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % paper.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\balancecolumns
% That's all folks!
\end{document}

>>>>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%\documentclass{acm_proc_article-sp}
\documentclass{sig-alternate}
\usepackage{url}
\hyphenation{Web-GL Java-Script Turtle-Script infra-structure}

\begin{document}

@@

\numberofauthors{1}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. Scott Ananian \qquad Chris J. Ball \qquad Michael Stone\titlenote{%
Now at Akamai Technologies.}\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{\{cscott,cjb,mstone\}@laptop.org}
%\and  % use '\and' if you need 'another row' of author names
}
\date{12 March 2012}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\conferenceinfo{IDC 2012,}{June 12--15, 2012, Bremen, Germany}
\CopyrightYear{2012}
\crdata{978-1-4503-1007-9}

% Copyright info
%\toappear{\textit{IDC 2012}, June 12--15, 2012, Bremen, Germany.\\
%Copyright 2012 ACM 978-1-4503-1007-9\ldots\$10.00.}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}

% ACM needs 'a single self-contained file'!
%\bibliography{paper}  % paper.bib is the name of the Bibliography in this case
\begin{thebibliography}{10}

\bibitem{aiml:2005}
{A.L.I.C.E. AI Foundation}.
\newblock Artificial intelligence markup language ({AIML}) version 1.0.1.
\newblock \url{http://www.alicebot.org/TR/2005/WD-aiml/}, 2005.

\bibitem{turtlescript}
C.~S. Ananian.
\newblock \url{http://cscott.net/Projects/TurtleScript/}, 2011.

\bibitem{bizzocchi:narrative}
J.~Bizzocchi.
\newblock Games and narrative: An analytical framework.
\newblock {\em Loading---the Journal of the Canadian Games Studies
  Association}, 1(1), 2007.

\bibitem{boyd:stories}
B.~Boyd.
\newblock {\em On the Origin of Stories: Evolution, Cognition, and Fiction}.
\newblock Belknap Press of Harvard University Press, 2009.

\bibitem{chang:tinkrbook}
A.~Chang and C.~Breazeal.
\newblock {TinkRBook}: Shared reading interfaces for storytelling.
\newblock In {\em Proc. of the 10th Int'l Conf. on Interaction Design and
  Children (IDC '11)}, pages 145--148. ACM, June 2011.

\bibitem{don:narrative}
A.~Don.
\newblock Narrative and the interface.
\newblock In B.~Laurel, editor, {\em The Art of Human-Computer Interface
  Design}, pages 383--391. Addison-Wesley, Reading, MA, 1990.

\bibitem{strips}
R.~E. Fikes and N.~J. Nilsson.
\newblock {STRIPS}: A new approach to the application of theorem proving to
  problem solving.
\newblock {\em Artificial Intelligence}, 2(3--4):189--208, 1971.

\bibitem{gardner:mi}
H.~E. Gardner.
\newblock {\em Frames Of Mind: The Theory of Multiple Intelligences}.
\newblock Basic Books, Dec. 1983.

\bibitem{lebowitz:universe85}
M.~Lebowitz.
\newblock Story-telling as planning and learning.
\newblock {\em Poetics}, 14(6):483--502, Dec. 1985.

\bibitem{montfort:curveship}
N.~Montfort.
\newblock Curveship's automatic narrative variation.
\newblock In {\em Proc. of the 6th Int'l Conf. on the Foundations of Digital
  Games (FDG '11)}, pages 211--218, June 2011.

\bibitem{powers:appleguide}
J.~Powers.
\newblock Giving users help with {A}pple {G}uide.
\newblock {\em develop}, 18, June 1994.
\newblock Apple Computer, Inc.

\bibitem{riedl:2008}
M.~O. Riedl, A.~Stern, D.~Dini, and J.~Alderman.
\newblock Dynamic experience management in virtual worlds for entertainment,
  education, and training.
\newblock {\em Int'l Trans. on Systems Science and Applications}, 3(1), 2008.

\bibitem{riedl:planning}
M.~O. Riedl and R.~M. Young.
\newblock Narrative planning: Balancing plot and character.
\newblock {\em Journal of Artificial Intelligence Research}, 39:217--267, 2010.

\bibitem{quasiquote}
M.~Samuel.
\newblock Ecmascript quasi-literals.
\newblock \url{http://wiki.ecmascript.org/doku.php?id=harmony:quasis}, 2012.

\bibitem{skorupski:2009}
J.~Skorupski and M.~Mateas.
\newblock Interactive story generation for writers: Lessons learned from the
  {W}ide {R}uled authoring tool.
\newblock In {\em Proc. of the 8th Digital Art and Culture Conf. (DAC)},
  Irvine, CA, Dec. 2009.

\bibitem{stefanakis:portfolios}
E.~Stefanakis.
\newblock {\em Multiple Intelligences and Portfolios: A Window Into The
  Learner's Mind}.
\newblock Heinemann, 2002.

\bibitem{sugar}
{Sugar Labs}.
\newblock \url{http://sugarlabs.org}.

\bibitem{turkle:alone}
S.~Turkle.
\newblock {\em Alone Together: Why We Expect More From Technology and Less From
  Each Other}.
\newblock Basic Books, 2011.

\bibitem{wilcox:2010}
B.~Wilcox.
\newblock Beyond {F}a\c{c}ade: Pattern matching for natural language
  applications.
\newblock
  \url{http://chatscript.sourceforge.net/Documentation/Pattern_Matching_for_Natural_Language_Applications.pdf},
  Feb. 2011.

\end{thebibliography}

%
%\balancecolumns
% That's all folks!
\end{document}
